Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-05-06 Supplemental-Material-A-Annotated-Analysis.Rmd
typo
study one and annotations added

---
title: "Supplemental Information A: Full Annotated Analysis and Reproducible Code"
subtitle: "Supplemental Material for 'Qualitative Goals'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/TBD" target="_blank">osf.io/TBD</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
#bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

<br/>

@@

```{r cleanWorker}
#  important names for Morning and Afternoon
names.m <- c(
  "StartDate",
  "EndDate",
  "Finished",
  "Duration__in_seconds_",
  "RecordedDate",
  "ExternalReference",
  "Meta_Operating_System",
  "Contact_dum",
  "number",
  "time",
  "duration_1",
  "dyad.group",
  "gr_size",
  "gr_type_1",
  "gr_type_2",
  "gr_type_3",
  "gr_type_4",
  "gr_type_5",
  "gr_type_6",
  "gr_type_7",
  "gr_type_8",
  "gr_type_9",
  "gr_type_10",
  "gr_type_11",
  "gr_type_12",
  "gr_type_13",
  "gr_type_14",
  "gr_type_15",
  "gr_type_16",
  "gr_type_17_TEXT",
  "gr_context_1",
  "gr_context_2",
  "gr_context_3",
  "gr_context_4",
  "gr_context_5",
  "gr_context_6",
  "gr_context_7",
  "gr_context_8",
  "gr_context_9",
  "gr_context_10",
  "gr_context_11",
  "gr_context_12",
  "gr_context_13_TEXT",
  "gr_context_14_TEXT",
  "gr_dutchness",
  "dyad_type_1",
  "dyad_type_2",
  "dyad_type_3",
  "dyad_type_4",
  "dyad_type_5",
  "dyad_type_6",
  "dyad_type_7",
  "dyad_type_8",
  "dyad_type_9",
  "dyad_type_10",
  "dyad_type_11",
  "dyad_type_12",
  "dyad_type_13",
  "dyad_type_14",
  "dyad_type_15",
  "dyad_type_16",
  "dyad_type_17_TEXT",
  "Context_1",
  "Context_2",
  "Context_3",
  "Context_4",
  "Context_5",
  "Context_6",
  "Context_7",
  "Context_8",
  "Context_9",
  "Context_10",
  "Context_11",
  "Context_12",
  "Context_13_TEXT",
  "Context_14_TEXT",
  "keyMotive",
  "keymotive_fulfillemt_1",
  "keyMotive_Dutch_1",
  "autonomy_1",
  "competence_1",
  "relatedness_self_1",
  "relatedness_other_1",
  "qualityAccidental_1",
  "qualityVoluntary_1",
  "qualityCooperative_1",
  "qualityDutchy_1",
  "quality_overall_1",
  "quality_meaning_1",
  "quality_star_1",
  "wantInt",
  "desire_type_1",
  "desire_type_2",
  "desire_type_3",
  "desire_type_4",
  "desire_type_5",
  "desire_type_6",
  "desire_type_7",
  "desire_type_8",
  "desire_type_9",
  "desire_type_10",
  "desire_type_11",
  "desire_type_12",
  "desire_type_13",
  "desire_type_14",
  "desire_type_15",
  "desire_type_16",
  "desire_type_17_TEXT",
  "desire_context_1",
  "desire_context_2",
  "desire_context_3",
  "desire_context_4",
  "desire_context_5",
  "desire_context_6",
  "desire_context_7",
  "desire_context_8",
  "desire_context_9",
  "desire_context_10",
  "desire_context_11",
  "desire_context_12",
  "desire_context_13_TEXT",
  "desire_context_14_TEXT",
  "Reason_nodesire",
  "keyMotive_noInt",
  "keyMotive_noInt_fulf_1",
  "autonomy_NoInt_1",
  "competence_NoInt_1",
  "relatedness_1_NoInt_1",
  "thermometerDutch_1",
  "thermometerDutchInt_2",
  "ExWB_1",
  "alertness1",
  "calmness1",
  "valence1",
  "alertness2",
  "calmness2",
  "valence2",
  "inNonDutch",
  "NonDutchNum",
  "NonDutchType_1",
  "NonDutchType_2",
  "NonDutchType_3",
  "NonDutchType_4",
  "NonDutchType_5",
  "NonDutchType_6",
  "NonDutchType_7",
  "NonDutchType_8",
  "NonDutchType_9",
  "NonDutchType_10",
  "NonDutchType_11",
  "NonDutchType_12",
  "NonDutchType_13",
  "NonDutchType_14",
  "NonDutchType_15_TEXT",
  "date",
  "time.0",
  "LocationLatitude",
  "LocationLongitude"
)

@@

# Need scales
df$keyMotiveFulfilled <- rowSums(df[, c("keymotive_fulfillemt_1", "keyMotive_noInt_fulf_1")], na.rm = T)
df$autonomy.daily.all <- rowSums(df[, c("autonomy_1", "autonomy_NoInt_1")], na.rm = T)
df$competence.daily.all <- rowSums(df[, c("competence_1", "competence_NoInt_1")], na.rm = T)
# cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
df$relatedness.daily.all <- rowMeans(df[, c(
  "relatedness_other_1",
  "relatedness_self_1",
  "relatedness_1_NoInt_1"
)], na.rm = T)

@@

@@

ggplot(df, aes(x = AllportsCondition)) +
  geom_histogram()

@@

@@

## Study 1 (Worker):

```{r workerDataSelection}

## Study 2 (Student):

@@

@@

@@

## Study 3 (Medical):

@@

@@

>>>>

---
title: "Supplemental Information A: Full Annotated Analysis and Reproducible Code"
subtitle: "Supplemental Material for 'Migration Trajectories [working title]'"
author:
- Jannis Kreienkamp^1,3^
- Kai Epstude^1,3^
- Laura F. Bringmann^1,3^
- Maximilian Agostini^1,3^
- Peter de Jonge^1,3^
- Rei Tendeiro-Monden^2,3^
- ^1^University of Groningen, Department of Psychology
- ^2^Hiroshima University, Graduate School of Advanced Science and Engineering
- ^3^Author order TBD [currently in first name alphabetical order]
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: j.kreienkamp@rug.nl"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/TBA" target="_blank">osf.io/TBA</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
#bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

@@

@@

```{r cleanWorker}
#  important names for Morning and Afternoon
names.m <- c(
  "StartDate",
  "EndDate",
  "Finished",
  "Duration__in_seconds_",
  "RecordedDate",
  "ExternalReference",
  "Meta_Operating_System",
  "Contact_dum",
  "number",
  "time",
  "duration_1",
  "dyad.group",
  "gr_size",
  "gr_type_1",
  "gr_type_2",
  "gr_type_3",
  "gr_type_4",
  "gr_type_5",
  "gr_type_6",
  "gr_type_7",
  "gr_type_8",
  "gr_type_9",
  "gr_type_10",
  "gr_type_11",
  "gr_type_12",
  "gr_type_13",
  "gr_type_14",
  "gr_type_15",
  "gr_type_16",
  "gr_type_17_TEXT",
  "gr_context_1",
  "gr_context_2",
  "gr_context_3",
  "gr_context_4",
  "gr_context_5",
  "gr_context_6",
  "gr_context_7",
  "gr_context_8",
  "gr_context_9",
  "gr_context_10",
  "gr_context_11",
  "gr_context_12",
  "gr_context_13_TEXT",
  "gr_context_14_TEXT",
  "gr_dutchness",
  "dyad_type_1",
  "dyad_type_2",
  "dyad_type_3",
  "dyad_type_4",
  "dyad_type_5",
  "dyad_type_6",
  "dyad_type_7",
  "dyad_type_8",
  "dyad_type_9",
  "dyad_type_10",
  "dyad_type_11",
  "dyad_type_12",
  "dyad_type_13",
  "dyad_type_14",
  "dyad_type_15",
  "dyad_type_16",
  "dyad_type_17_TEXT",
  "Context_1",
  "Context_2",
  "Context_3",
  "Context_4",
  "Context_5",
  "Context_6",
  "Context_7",
  "Context_8",
  "Context_9",
  "Context_10",
  "Context_11",
  "Context_12",
  "Context_13_TEXT",
  "Context_14_TEXT",
  "keyMotive",
  "keymotive_fulfillemt_1",
  "keyMotive_Dutch_1",
  "autonomy_1",
  "competence_1",
  "relatedness_self_1",
  "relatedness_other_1",
  "qualityAccidental_1",
  "qualityVoluntary_1",
  "qualityCooperative_1",
  "qualityDutchy_1",
  "quality_overall_1",
  "quality_meaning_1",
  "quality_star_1",
  "wantInt",
  "desire_type_1",
  "desire_type_2",
  "desire_type_3",
  "desire_type_4",
  "desire_type_5",
  "desire_type_6",
  "desire_type_7",
  "desire_type_8",
  "desire_type_9",
  "desire_type_10",
  "desire_type_11",
  "desire_type_12",
  "desire_type_13",
  "desire_type_14",
  "desire_type_15",
  "desire_type_16",
  "desire_type_17_TEXT",
  "desire_context_1",
  "desire_context_2",
  "desire_context_3",
  "desire_context_4",
  "desire_context_5",
  "desire_context_6",
  "desire_context_7",
  "desire_context_8",
  "desire_context_9",
  "desire_context_10",
  "desire_context_11",
  "desire_context_12",
  "desire_context_13_TEXT",
  "desire_context_14_TEXT",
  "Reason_nodesire",
  "keyMotive_noInt",
  "keyMotive_noInt_fulf_1",
  "autonomy_NoInt_1",
  "competence_NoInt_1",
  "relatedness_1_NoInt_1",
  "thermometerDutch_1",
  "thermometerDutchInt_2",
  "ExWB_1",
  "MDMQ.v1_1",
  "MDMQ.v1_2",
  "MDMQ.v1_3",
  #"MDMQ.v1_3r",
  "MDMQ.v1_4",
  #"MDMQ.v1_4r",
  "MDMQ.v1_5",
  #"MDMQ.v1_5r",
  "MDMQ.v1_6",
  "MDMQ.v1_7",
  #"MDMQ.v1_7r",
  "MDMQ.v1_8",
  "MDMQ.v1_9",
  #"MDMQ.v1_9r",
  "MDMQ.v1_10",
  "MDMQ.v1_11",
  #"MDMQ.v1_11r",
  "MDMQ.v1_12",
  "MDMQ.v1_13",
  "MDMQ.v2_1",
  #"MDMQ.v2_1r",
  "MDMQ.v2_2",
  "MDMQ.v2_3",
  "MDMQ.v2_4",
  #"MDMQ.v2_4r",
  "MDMQ.v2_5",
  "MDMQ.v2_6",
  #"MDMQ.v2_6r",
  "MDMQ.v2_7",
  #"MDMQ.v2_7r",
  "MDMQ.v2_8",
  "MDMQ.v2_9",
  "MDMQ.v2_10",
  #"MDMQ.v2_10r",
  "MDMQ.v2_11",
  #"MDMQ.v2_11r",
  "MDMQ.v2_12",
  "MDMQ.v2_13",
  "alertness1",
  "calmness1",
  "valence1",
  "alertness2",
  "calmness2",
  "valence2",
  "inNonDutch",
  "NonDutchNum",
  "NonDutchType_1",
  "NonDutchType_2",
  "NonDutchType_3",
  "NonDutchType_4",
  "NonDutchType_5",
  "NonDutchType_6",
  "NonDutchType_7",
  "NonDutchType_8",
  "NonDutchType_9",
  "NonDutchType_10",
  "NonDutchType_11",
  "NonDutchType_12",
  "NonDutchType_13",
  "NonDutchType_14",
  "NonDutchType_15_TEXT",
  "date",
  "time.0",
  "LocationLatitude",
  "LocationLongitude"
)

@@

# Make time IDs consistent with later studies
df$TID <- paste(df$PPDate, str_to_title(df$daytime))
df$TIDnum <- as.numeric(factor(df$TID %>% gsub(" Morning", "-A", .) %>% gsub(" Afternoon", "-B", .)))

# Make contact dummies consistent with later studies
df$IntergroupContact <- df$Contact_dum

df <- df %>%
  rowwise() %>%
  mutate(
    InteractionDum = sum(Contact_dum, inNonDutch, na.rm = FALSE),
    InteractionDum = if_else(InteractionDum > 0, 1, InteractionDum),
    alertness = sum(alertness1, alertness2, na.rm = TRUE),
    calmness = sum(calmness1, calmness2, na.rm = TRUE),
    valence = sum(valence1, valence2, na.rm = TRUE)
  ) %>%
  ungroup()

# Need scales
df$InteractionNeedFullfillment <- df$keymotive_fulfillemt_1
df$DaytimeNeedFullfillment <- df$keyMotive_noInt_fulf_1

df$keyMotiveFulfilled <- rowSums(df[, c("keymotive_fulfillemt_1", "keyMotive_noInt_fulf_1")], na.rm = T)
df$autonomy.daily.all <- rowSums(df[, c("autonomy_1", "autonomy_NoInt_1")], na.rm = T)
df$competence.daily.all <- rowSums(df[, c("competence_1", "competence_NoInt_1")], na.rm = T)
# cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
df$relatedness.daily.all <- rowMeans(df[, c(
  "relatedness_other_1",
  "relatedness_self_1",
  "relatedness_1_NoInt_1"
)], na.rm = T)

@@

df$Autonomy <- df$autonomy.daily.all
df$Competence <- df$competence.daily.all
df$Relatedness <- df$relatedness.daily.all

# Make Outgroup Attitudes consistent with later studies
df$AttitudesDutch <- df$thermometerDutch_1
df$AttitudesPartner <- df$thermometerDutchInt_2

# Make experienced well-being consistent with later studies
df$ExWB <- df$ExWB_1

@@

ggplot(df, aes(x = AllportsCondition)) +
  geom_histogram() +
  theme_Publication()

@@

As one of our main analyses is a three-mode principal component analysis (3MPCA) we begin by assessing the amount of missing data in each of the ESM studies. To assess the missingness in detail, we prepare a data availability table of whether data is available or missing for each possible measurement point (data + morning/afternoon) for all individual participants. We then export the data availability tables as comma separated value files (.csv) to be assessed in detail using a spreadsheet program (such as MS Excel).

@@

The three-mode PCA ultimately aims to explain the most variance with the fewest components (by maximizing the variance of data mapped in a lower dimensional space --- often by maximally separating groups of cases with similar variable patterns). Importantly, this procedure depends on variances and covariances to be present within the data. As one of our three modes is time and variance over time is not always given (e.g., because a variable is stable over the measured time span, such as personality over a month), it becomes important to assess whether a dimension reduction is possible for the variables measured during the measured time period. We, thus, start by visually inspecting the average changes and variance developments of all potentially relevant variables. We hope so see changes within the means and standard deviations over the measurement period.

## Study 1 (Worker)

The first study, utilized not only the smallest sample but also a slightly different set of measured variables compared to the later two studies. Several variables are consistent across all three studies (e.g., types of social interactions, interaction needs, self-determiantion theory needs, outgroup attitudes, and experienced well-being). Study 1 additionally included several emotion and mood measurements but fewer cognitive and behavioral measures than studies two and three.

We first select all potentially relevant variables and their labels, and then group the variables in small groups of one to three variables for plotting.

```{r workerDataSelection}
varListWorker <- 
  c(
    "IntergroupContact",
    "InteractionDum",
    "DaytimeNeedFullfillment",
    "InteractionNeedFullfillment",
    "Autonomy",
    "Competence",
    "Relatedness",
    "AttitudesDutch",
    "AttitudesPartner",
    "ExWB",
    "alertness",
    "calmness",
    "valence",
    "MDMQ.v1_1",
    "MDMQ.v1_2",
    "MDMQ.v1_3",
    "MDMQ.v1_4",
    "MDMQ.v1_5",
    "MDMQ.v1_6",
    "MDMQ.v1_7",
    "MDMQ.v1_8",
    "MDMQ.v1_9",
    "MDMQ.v1_10",
    "MDMQ.v1_11",
    "MDMQ.v1_12",
    "MDMQ.v1_13",
    "MDMQ.v2_1",
    "MDMQ.v2_2",
    "MDMQ.v2_3",
    "MDMQ.v2_4",
    "MDMQ.v2_5",
    "MDMQ.v2_6",
    "MDMQ.v2_7",
    "MDMQ.v2_8",
    "MDMQ.v2_9",
    "MDMQ.v2_10",
    "MDMQ.v2_11",
    "MDMQ.v2_12",
    "MDMQ.v2_13"
  )

varNameListWorker <- 
  c(
    "IntergroupContact" = "Dutch Interaction",
    "InteractionDum" = "Any Interaction",
    "DaytimeNeedFullfillment" = "Daytime Core Motive Fulfillment",
    "InteractionNeedFullfillment" = "Interaction Core Motive Fulfillment",
    "Autonomy" = "Autonomy",
    "Competence" = "Competence",
    "Relatedness" = "Relatedness",
    "AttitudesDutch" = "Outgroup Attitude",
    "AttitudesPartner" = "Attitude Interaction Partner",
    "ExWB" = "Sadness Happiness",
    "alertness" = "Alertness",
    "calmness" = "Calmness",
    "valence" = "Emotional Valence",
    "MDMQ.v1_1" = "content",
    "MDMQ.v1_2" = "rested",
    "MDMQ.v1_3" = "restless",
    "MDMQ.v1_4" = "bad",
    "MDMQ.v1_5" = "worn-out",
    "MDMQ.v1_6" = "composed",
    "MDMQ.v1_7" = "tired",
    "MDMQ.v1_8" = "great",
    "MDMQ.v1_9" = "uneasy",
    "MDMQ.v1_10" = "energetic",
    "MDMQ.v1_11" = "uncomfortable",
    "MDMQ.v1_12" = "relaxed",
    "MDMQ.v1_13" = "alive and vital",
    "MDMQ.v2_1" = "sleepy",
    "MDMQ.v2_2" = "good",
    "MDMQ.v2_3" = "at ease",
    "MDMQ.v2_4" = "unhappy",
    "MDMQ.v2_5" = "alert",
    "MDMQ.v2_6" = "discontent",
    "MDMQ.v2_7" = "tense",
    "MDMQ.v2_8" = "fresh",
    "MDMQ.v2_9" = "happy",
    "MDMQ.v2_10" = "nervous",
    "MDMQ.v2_11" = "exhausted",
    "MDMQ.v2_12" = "calm",
    "MDMQ.v2_13" = "alive and vital"
  )

dtWorker$viz <- list()

dtWorker$vizall <- dtWorker$full %>%
  select(
    PID,
    TID,
    TIDnum,
    all_of(varListWorker)
  )

dtWorker$viz$Interaction <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    IntergroupContact,
    InteractionDum
  )

dtWorker$viz$KeyNeed <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    DaytimeNeedFullfillment,
    InteractionNeedFullfillment
  )

dtWorker$viz$SDT <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    Autonomy,
    Relatedness, 
    Competence
  )

dtWorker$viz$Attitudes <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    starts_with("Attitudes")
  )

dtWorker$viz$WB <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    ExWB
  )

dtWorker$viz$MoodOverall <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    alertness,
    calmness,
    valence
  )

dtWorker$viz$MoodV01Pt01 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_1,
    MDMQ.v1_2
  )

dtWorker$viz$MoodV01Pt02 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_3,
    MDMQ.v1_4
  )

dtWorker$viz$MoodV01Pt03 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_5,
    MDMQ.v1_6
  )

dtWorker$viz$MoodV01Pt04 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_7,
    MDMQ.v1_8
  )

dtWorker$viz$MoodV01Pt05 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_9,
    MDMQ.v1_10
  )

dtWorker$viz$MoodV01Pt06 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v1_11,
    MDMQ.v1_12,
    MDMQ.v1_13
  )

dtWorker$viz$MoodV02Pt01 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_1,
    MDMQ.v2_2
  )

dtWorker$viz$MoodV02Pt02 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_3,
    MDMQ.v2_4
  )

dtWorker$viz$MoodV02Pt03 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_5,
    MDMQ.v2_6
  )

dtWorker$viz$MoodV02Pt04 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_7,
    MDMQ.v2_8
  )

dtWorker$viz$MoodV02Pt05 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_9,
    MDMQ.v2_10
  )

dtWorker$viz$MoodV02Pt06 <- dtWorker$vizall %>%
  select(
    PID,
    TID,
    TIDnum,
    MDMQ.v2_11,
    MDMQ.v2_12,
    MDMQ.v2_13
  )
```

We begin by plotting the item means of all variables. We always only display one to three variables jointly to improve visual inspection. We plot the means of the individual variables for each measurement occasion, summarizing the responses of all participants at any given time point. We additionally plot the data availability of each variable as a marginal plot above the main plot. The displayed time axis is the measurement index rather than the actual date to ensure comparability of the changes between each measurement. Plots with the raw date-time axis are saved and can be displayed if necessary.

```{r workerMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtWorker$vizPlotsMean <-
  lapply(seq_along(dtWorker$viz),
         function(i)
           statVarPlot(dataIn = dtWorker$viz[[i]], 
                       name = names(dtWorker$viz)[[i]], 
                       namList = varNameListWorker,
                       stat = "mean")
         )
dtWorker$vizPlotsMean
```

To illustrate the developments of variance around the previously displayed means, we then plot the item standard deviations of all variables. We, thus, plot the average variation from the mean for each individual variable, again summarizing the responses of all participants at any given time point. We retain the same variable grouping, the data availability line plot, and the measurement index as the x axis.

```{r WorkerSdViz, echo=FALSE, results='hide',fig.keep='all'} 
dtWorker$vizPlotsSd <-
  lapply(seq_along(dtWorker$viz),
         function(i)
           statVarPlot(dataIn = dtWorker$viz[[i]], 
                       name = names(dtWorker$viz)[[i]], 
                       namList = varNameListWorker,
                       stat = "sd")
         )
dtWorker$vizPlotsSd
```

## Study 2 (Student)

During the second study we collected the largest sample and additionally collected a range of motivations as well as pro-social and anti-social behaviors.

We, again, select all potentially relevant variables and their labels, and then group the variables in small groups of one to three variables for plotting.

@@

We again begin by plotting the item means of all variables. The plotting method is identical to that of Study 1.

@@

We then also plot the average variation around the mean for each time point and variable. The plotting method is identical to that of Study 1.

@@

## Study 3 (Medical)

The third study uses a similar set up as Study 2 but targets a more vulnerable sample (of young medical professionals). While most key variables are identical to Study 2, in this last study we additionally collected several cognitive evaluations (e.g., importance ratings) and emotional status measures (e.g., anger, nervousness, energy, and loneliness).

We, again, select all potentially relevant variables and their labels, and then group the variables in small groups of one to three variables for plotting.

@@

As with the previous studies, we begin by plotting the item means of all variables. The plotting method is identical to that of Studies 1 and 2.

@@

Lastly, also again plot the item standard deviations of all variables at each time point. The plotting procedures are again identical to Studies 1 and 2.
